---
title: "Lab 9 Mireia Valle"
author: "Mireia Valle"
date: "04/03/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

Loading required libraries
```{r}
library(tidyverse)
library(here)
library(janitor)
library(boot)
#install.packages("patchwork")
library(patchwork)
library(broom)
#install.packages("nlstools")
library(nlstools)
```

Get the dev version of gt from github after attaching devtools
```{r}
library(devtools)
remotes::install_github("rstudio/gt")
library(gt)
```

### Fun tables with "gt"

```{r}
LifeCycleSavings
?LifeCycleSavings
```

Convert  row names to a column and convert to decimal the percentage values of dpi

```{r}
disp_income <- LifeCycleSavings %>% 
  rownames_to_column() %>% 
  arrange(dpi) %>% 
  head(5) %>% 
  mutate(ddpi = ddpi / 100, 
         pop15 = pop15 / 100, 
         pop75 = pop75 / 100)

  
```
Now let's make a nice table with "gt"

```{r}
disp_income %>% 
  gt()
```

we want to customize the table adding a title and a subtitle

```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", 
    subtitle = "5 countries with the lowest per capita dispossable income") 
```

We want to change the format of the currency

```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", 
    subtitle = "5 countries with the lowest per capita dispossable income") %>% 
  fmt_currency(
    columns = vars(dpi),
    decimals = 2)
```

We want to change the format to decimals
```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", 
    subtitle = "5 countries with the lowest per capita dispossable income") %>% 
  fmt_currency(
    columns = vars(dpi),
    decimals = 2) %>% 
  fmt_percent(
    columns = vars (pop15, pop75, ddpi),
    decimals = 1)
```
Changing the width
```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", 
    subtitle = "5 countries with the lowest per capita dispossable income") %>% 
  fmt_currency(
    columns = vars(dpi),
    decimals = 2) %>% 
  fmt_percent(
    columns = vars(pop15, pop75, ddpi),
    decimals = 1)  ) %>% 
  tab_options(
    table.width = pct(80))
  
```
Adding a foot note

```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", 
    subtitle = "5 countries with the lowest per capita dispossable income") %>% 
  fmt_currency(
    columns = vars(dpi),
    decimals = 2) %>% 
  fmt_percent(
    columns = vars(pop15, pop75, ddpi),
    decimals = 1)  ) %>% 
  tab_options(
    table.width = pct(80)) %>% 
  tab_footnote(
    footnote = "Data averaged from 1970 - 1980"
    location = cells_title())
  
```

Adding colors

```{r}
disp_income %>% 
  gt() %>% 
  tab_header(
    title = "Life cycle savings", # Add a title
    subtitle = "5 countries with lowest per capita disposable income" # And a subtitle
  ) %>% 
  fmt_currency( # Reformat to currency notation...
    columns = vars(dpi), # The values for the 'Height' variable
    decimals = 2 # Keeping 3 decimal places
  ) %>% 
  fmt_percent(
    columns = vars(pop15, pop75, ddpi),
    decimals = 1
  ) %>% 
  fmt_number(
    columns = vars(sr),
    decimals = 1
  ) %>% 
  tab_options(
    table.width = pct(80)
  ) %>% 
  tab_footnote(
    footnote = "Data averaged from 1970 - 1980",
    location = cells_title()
  ) %>% 
  data_color( # Update cell colors...
    columns = vars(dpi), # ...for mean_len column
    colors = scales::col_numeric(
      palette = c(
        "orange", "red", "purple"), # Overboard colors! 
      domain = c(120,190) # Scale endpoints (outside will be gray)
  )
  )
```

## Bootstrap the confidence interval of salinity



```{r}
view(salinity)

hist(salinity$sal)

gplot(data = salinity, aes(sample=sal)) + 
  geom_qq()

t.test(salinity$sal) # Get 95% CI for t-distribution
```

But I really want to compare this by using bootstraping to find a sampling distribution based on my data, instead of based enterily in assumptions


Create a function to calculate the mean of different bootstrap samples:


```{r}
# First, create a function that will calculate the median of each bootstrapped sample
mean_fun <- function (x,i) {mean(x[i])}

# Then, get just the vector of salinity (salinity$sal)
sal_nc <- salinity$sal

#we bootstrap the salinity vector

set.seed(5002)

salboot_100 <- boot(data = sal_nc, 
                    statistic = mean_fun,
                    R = 100)
salboot_100

salboot_100$t

#bias tell as how different is the mean from our bootstrap sample compared to the original

salboot_10k <- boot(data = sal_nc, 
                    statistic = mean_fun,
                    R = 1000)

```

Ploting the means

We convert to dataframe to plot it using ggplot

```{r}
salboot_100_df <- data.frame(bs_mean = salboot_100$t)
salboot_10k_df <- data.frame(bs_mean = salboot_10k$t)
```
#Now let's plot the bootstraping sampling distribution:

```{r}
p1 <- ggplot(data = salinity, aes(x=sal))+
  geom_histogram()

p2 <- ggplot(data = salboot_100_df, aes(x = bs_mean))+
  geom_histogram()

p3 <- ggplot(data = salboot_10k_df, aes(x = bs_mean))+
  geom_histogram()
```
Ploting the 3 hist using patchwork

```{r}
p1 + p2 + p3
```

reordering the graphs

```{r}
p1 + p2 /p3
```

```{r}
(p1 + p2) /p3
```

Calculating the confidence interval

```{r}
boot.ci(salboot_10k, conf = 0.95)
```

###Example of non linear least square

Loading the data

```{r}
df <- read_csv(here("data", "log_growth.csv"))
```

plot it
```{r}
ggplot(data = df, aes(x = time, y = pop)) +
  geom_point()
```

plot it's log distribution
```{r}
ggplot(data = df, aes(x = time, y = log(pop))) +
  geom_point()
```


```{r}
df_exp <- df %>% 
  filter(time < 15) %>% 
  mutate(ln_pop = log(pop))


lm_k <- lm(ln_pop ~ time, data = df_exp)

# lm_k
# Estimate: growth reate = 0.17
# K = 180
# A = 18
```

Now, NLS: 

```{r}
df_nls <- nls(pop ~ K/(1 + A*exp(-r*time)),
              data = df, 
              start = list (K = 180, A = 18, r = 0.17), #initial values of the parameters
              trace = TRUE) #to see the iteractive process

summary(df_nls)

model_out <- broom::tidy(df_nls)
model_out
```

creating a sequence
```{r}
t_seq <- seq(from = 0, to = 35, length = 200)
```

make a prediction from our nls model using the sequence of time

```{r}
p_predict <- predict(df_nls, newdata= t_seq)

view(p_predict)
```

Bind together time and prediction data

```{r}
df_complete <- data.frame(df, p_predict)
```

Plot 

```{r}
ggplot(data = df_complete, aes(x = time, y = pop)) +
  geom_point() +
  geom_line(aes(x = time, y = p_predict))+
  theme_minimal()
```

The equation:

P(t) = 189 / 1 + 138 e^-035*times

calculating the ci
```{r}
df_ci <- confint2(df_nls)
df_ci
```

